RSV

### 2018-01-15 Analysis/RSV.Rmd
Changed calendar to use epi year; added sliding window analysis

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")

source("./RSV.R")
```

@@

```{r warning=FALSE}
obsByCountyYear = dataset %>% 
  rename(time=weekofyear) %>% 
  group_by(county, weeki, year, time) %>% 
  summarize(rsv=sum(rsv)) %>% 
  left_join(rsvCountyGroups, by="county") %>%
  group_by(weeki, year, time) %>%
  do(summarizeCountyGroups(.)) %>%
  group_by(county, year) %>%
  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / if_else(sum(rsv) > 0, sum(rsv), as.integer(1))) %>% 
  select(-weeki) %>%
  as.data.frame()

predByCountyYear = data.frame()
thresholdsByCountyYear = data.frame()
slidingStratUnprotectedSimByCountyYear = data.frame()

progress = txtProgressBar(max=length(levels(obsByCounty$county)) * length(rsvYears) * 2, style=3)
idx = 0

for (c in levels(obsByCountyYear$county)) {
  for (y in rsvYears) {
    countyYearObs = obsByCountyYear %>% filter(county==c, year==y)
    countyYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=countyYearObs)

    countyYearPred = countyYearModel %>% 
      predict(type="response", newdata=data.frame(time=modelTime), se.fit=TRUE)

    countyYearPred = data.frame(time=modelTime) %>% 
      cbind(data.frame(rsv.fit=countyYearPred$fit, rsv.fit.se=countyYearPred$se.fit)) %>%
      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, outbreak.calc.cum())) %>%
      rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

    predByCountyYear = predByCountyYear %>% rbind(countyYearPred)

    countyYearThresholds = countyYearModel %>%
      outbreak.predict.scalars(
        modelTime,
        outbreak.calc.thresholds(onset=seasonThreshold, offset=1 - seasonThreshold)
      ) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

    thresholdsByCountyYear = thresholdsByCountyYear %>% rbind(countyYearThresholds)

    if (y %in% rsvWindowYears) {
      countyYearUnprotectedSim = countyYearModel %>%
        outbreak.predict.scalars.sim(
          modelTime,
          outbreak.calc.unprotected(ppxSlidingStrategies(c, y))
        ) %>%
        mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

      slidingStratUnprotectedSimByCountyYear = slidingStratUnprotectedSimByCountyYear %>% rbind(countyYearUnprotectedSim)
    }

    idx = idx + 1
    setTxtProgressBar(progress, idx)
  }
}

# Aggregate sliding strategies over the entire time span

unprotectedByCounty = slidingStratUnprotectedSimByCountyYear %>% 
  group_by(county, outbreak.sim) %>%
  summarize_at(vars(contains("total"), contains("count")), sum) %>%
  group_by(county, outbreak.sim) %>%
  do((function(df) {
    stratNames = names(ppxSlidingStrategies())
    for (stratName in stratNames) {
      countName = sprintf("%s.count", stratName)
      fracName = sprintf("%s.frac", stratName)
      df = df %>% 
        mutate_at(fracName, function(.) { df[[countName]] / df$total })
    }
    df
  }) (.)) %>%
  group_by(county) %>%
  do((function(df) {
    df %>%
      select(-county, -total, -matches(".count")) %>%
      outbreak.predict.scalars.confints () %>%
      mutate(county=unique(df$county))
  })(.)) %>%
  inner_join(fixedStratUnprotectedByCounty, by="county")
```

>>>>

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")
```
```{r}
source("./RSV.R")
```

@@
